Empirical Analysis of the Role of Energy in Economic Growth

### 2013-01-30 EconGrowth.Rnw
Now factors of production graph is exactly as I want it.

<<Country Factors Graph, echo=FALSE>>=
createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}
@
<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="Factors of Production for All Countries. (China's indexed capital stock rises to $k = 9.2$ in 2011.)", echo=FALSE>>=
createFactorsLatticeGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 3) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(2, 2, 1, 1, 1) #line widths
  colors <- c("black", "black", "red", "blue", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                  index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
                  type=graphType,
                  layout=c(3,3),
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           cex=0.85,
                           lines=lineSpec,
                           columns=1, x=0.01, y=0.95),
                  scales=list(cex=0.75, #controls text size on scales
                              tck=-0.5, #controls tick mark length
                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), 
                  ylim=c(0.5,4.5),
                  xlab="",
                  ylab="Indexed (1980=1 or 1991=1)")
  return(graph)
}
createFactorsLatticeGraph("All") #Reads data from the "AllData.txt" file.
@

>>>>

<<Country Factors Graph, echo=FALSE>>=
createCountryFactorsGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "l"
  lineTypes <- c(1, 5, 2, 4, 6) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(1, 1, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "black", "black") #line and point colors
  lineSpec <- list(lty=lineTypes, lwd=lineWidths, col=colors)
  graph <- xyplot(iCapStk+iLabor+iQ+iX+iU ~ Year, data=dataTable,
                  type=graphType,
                  par.settings = list(superpose.line = lineSpec),
                  key=list(text=list(c("k", "l", "q", "x", "u")),
                           type=graphType,
                           lines=lineSpec,
                           columns=1, x=0.0, y=0.98),
                  scales=list(cex=1.0, #controls text size on scales
                              tck=-0.5), #controls tick mark length
                  ylab="Indexed (1980=1)")
  return(graph)
}
@
<<Factors Lattice Graph, fig.width=6.5, fig.height=7.5, fig.cap="GDP ($y$), capital stock ($k$), labor ($l$), thermal energy ($q$), exergy ($x$), and useful work ($u$) for all economies. (China's indexed GDP and indexed capital stock rise to $y = 7.3$ and $k = 9.2$ in 2011.)", echo=FALSE>>=
createFactorsLatticeGraph <- function(countryName){
  dataTable <- loadData(countryName)
  graphType <- "b"
  lineTypes <- c(0, 1, 5, 2, 4, 1) #line types. See http://en.wikibooks.org/wiki/R_Programming/Graphics
  lineWidths <- c(0, 2, 2, 1, 1, 1) #line widths
  colors <- c("black", "black", "black", "red", "blue", "black") #line and point colors
  #symbols <- c("o", "", "", "", "", "")
  symbols <- c(1, NA_integer_, NA_integer_, NA_integer_, NA_integer_, NA_integer_)  
  lineSpec <- list(lty=lineTypes, lwd=lineWidths)
  graph <- xyplot(iGDP+iCapStk+iLabor+iQ+iX+iU ~ Year | Country, data=dataTable,
                  index.cond=list(c(7,6,3,1,8,5,4,2,9)), #orders the panels. Default is alphabetical.
                  as.table=TRUE, #indexing of panels starts in upper left and goes across rows.
                  type=graphType,
                  layout=c(3,3),
                  lty = lineTypes, lwd = lineWidths, col = colors, #Controls line parameters
                  pch = symbols, col.symbol = colors, #Controls symbol parameters
                  key=list(text=list(c("y", "k", "l", "q", "x", "u")),
                           type=graphType,
                           cex=0.85,
                           lines=lineSpec,
                           pch=symbols,
                           col=colors,
                           columns=1, x=0.01, y=0.95),
                  scales=list(cex=0.75, #controls text size on scales
                              tck=-0.5, #controls tick mark length
                              y=list(at=c(1,2,3,4,5,6,7,8,9,10))), 
                  ylim=c(0.5,4.5),
                  xlab="",
                  ylab="Indexed (1980=1 or 1991=1)")
  return(graph)
}
createFactorsLatticeGraph("All") #Reads data from the "AllData.txt" file.
@
